\hypertarget{monster0506s-dotfiles}{%
\section{Monster0506's Dotfiles}\label{monster0506s-dotfiles}}

These are my personal dotfiles, configured to my tastes. Feel free to
copy, change, remove, or ignore these.

\hypertarget{installation}{%
\subsection{Installation}\label{installation}}

Please do not install these files without understanding what they do or
what they are intended for. These files are mainly intended for setting
up a new installation.

However, for ease of configuration, it does move current setup files
into *.back, as not to overwrite them.

To use, run \texttt{bash\ bootstrap.sh} in the directory in which you
cloned or downloaded this repository.

\hypertarget{follow-up-steps}{%
\subsubsection{Follow-Up Steps}\label{follow-up-steps}}

Yes, these could be in a bootstrap, but I am too lazy to do that.

\begin{itemize}
\tightlist
\item
  Install starship

  \begin{itemize}
  \tightlist
  \item
    \texttt{curl\ -sS\ https://starship.rs/install.sh\ \textbar{}\ sh}
  \end{itemize}
\item
  Install Python
  \href{https://www.python.org/ftp/python/3.10.4/Python-3.10.4.tgz}{(latest
  version)}
\item
  Install Node

  \begin{itemize}
  \tightlist
  \item
    \texttt{curl\ -fsSL\ https://fnm.vercel.app/install\ \textbar{}\ bash}
  \item
    \texttt{fnm\ install\ {[}Version\ Number\ (16.15.0){]}}
  \end{itemize}
\item
  \texttt{sudo\ apt\ install\ vim\ neovim\ vim-gtk3\ fzf\ i3\ -y}
\item
  Install ruby from
  \href{https://cache.ruby-lang.org/pub/ruby/3.1/ruby-3.1.2.tar.gz}{here}
\item
  Install vim-plug

  \begin{itemize}
  \tightlist
  \item
    \texttt{sh\ -c\ \textquotesingle{}curl\ -fLo\ "\$\{XDG\_DATA\_HOME:-\$HOME/.local/share\}"/nvim/site/autoload/plug.vim\ -\/-create-dirs\ \textbackslash{}\ \ \ \ \ https://raw.githubusercontent.com/junegunn/vim-plug/master/plug.vim\textquotesingle{}}
  \end{itemize}
\item
  Install COC extentions via coc-marketplace

  \begin{itemize}
  \tightlist
  \item
    coc-pyright
  \item
    coc-snippets
  \item
    coc-lua
  \end{itemize}
\item
  Install useful python tools

  \begin{itemize}
  \tightlist
  \item
    \texttt{python3\ -m\ pip\ install\ setuptools}
  \item
    \texttt{pip3\ install\ black}
  \item
    \texttt{sudo\ apt\ install\ flake8\ pylint\ -y}
  \end{itemize}
\end{itemize}

\hypertarget{contents}{%
\subsection{Contents}\label{contents}}

I keep a pretty minimal configuration, but if I find something that I
like, I often add it to my dotfiles for later usage.

As a shell, I use bash with the \href{https://starship.rs}{starship}
prompt, and, as such, there is a starship configuration file there. I
don't often change those settings.

\hypertarget{vim-plugins}{%
\subsubsection{ViM Plugins}\label{vim-plugins}}

May be out-dated

\begin{itemize}
\tightlist
\item
  \href{https://preservim/nerdtree}{preservim/nerdtree}
\item
  \href{https://github.com/morhetz/gruvbox}{morhetz/gruvbox}
\item
  \href{https://github.com/neoclide/coc.nvim}{neoclide/coc.nvim}
\item
  \href{https://github.com/easymotion/vim-easymotion}{easymotion/vim-easymotion}
\item
  \href{https://github.com/sbdchd/neoformat}{sbdchd/neoformat}
\item
  \href{https://github.com/ryanoasis/vim-devicons}{ryanoasis/vim-devicons}
\item
  \href{https://github.com/preservim/nerdcommenter}{preservim/nerdcommenter}
\item
  \href{https://github.com/tpope/vim-repeat}{tpope/vim-repeat}
\item
  \href{https://github.com/tpope/vim-surround}{tpope/vim-surround}
\item
  \href{https://github.com/mg979/vim-visual-multi}{mg979/vim-visual-multi}
\item
  \href{https://github.com/mattn/emmet-vim}{mattn/emmet-vim}
\item
  \href{https://github.com/ap/vim-css-color}{ap/vim-css-color}
\item
  \href{https://github.com/vim-airline/vim-airline}{vim-airline/vim-airline}
\item
  \href{https://github.com/kien/ctrlp.vim}{kien/ctrlp.vim}
\item
  \href{https://github.com/sheerun/vim-polyglot}{sheerun/vim-polyglot}
\item
  \href{https://github.com/vim-syntastic/syntastic}{vim-syntastic/syntastic}
\end{itemize}
